### 2014-03-13 Draft/abstract.tex
Updated abstract, Intro, eval

\begin{abstract}
Temporal specifications of an Application Programming
Interface (API) describe allowed sequence of invocations
of methods within an API. Despite being desirable for 
software testing and verification (through formal analysis tools),
most API's do not have formal temporal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
Although existing techniques infer from API documents method specifications (such as method precondition and postconditions) or resource specifications (such as constraints on creating/releasing resources), such techniques fail to explicitly infer temporal constraints.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool,
to infer formal temporal specifications from natural language text of API documents.
\tool\ uses 
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
Our evaluation results show that \tool\ achieves an average of 66\% precision and 70\% recall
in inferring 69 temporal constraints from more than 3900 sentences of API documents.

>>>>

\begin{abstract}
Temporal specifications of an Application Programming
Interface (API) describe allowed sequence of invocations
of methods within an API. Despite being desirable for 
software testing and verification (through formal analysis tools),
most API's do not have formal temporal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
However, manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
There are existing techniques that infer from API documents resource specifications 
(such as constraints based on phases: creating, manipulating, and releasing resources).
However, such techniques are limited to finding temporal specification of resources.
Furthermore, such techniques do not make a distinction between explicit ordering of methods
within each phases. 
To address this issue, we propose a natural language processing based automated approach \tool,
to infer formal temporal specifications from natural language text of API documents.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
Our evaluation results show that \tool\ achieves an average of 65\% precision and 72\% recall
in inferring 63 temporal constraints from more than 3900 sentences of API documents.

### 2014-03-13 Draft/conclusion.tex
Updated abstract, Intro, eval

Although highly desirable, most API's do not have formal specifications.
In contrast documentation of methods contain detailed specifications of the usage in natural language text.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we proposed a novel approach \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
in inferring TT temporal constraints from more than ZZZZ sentences of API documents.

>>>>

Although highly desirable, most API's do not have formal specifications.
In contrast documentation of methods contain detailed specifications of the usage in natural language text.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we proposed a novel approach \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of 65\% precision and 72\% recall
in inferring 63 temporal constraints from more than 3900 sentences of API documents.

### 2014-03-13 Draft/evaluation.tex
Updated abstract, Intro, eval

\begin{enumerate}
	\item $TP$: A sentence correctly identified by \tool\ as constraint sentence.
	\item $FP$: A sentence incorrectly identified by \tool as constraint sentence.
	\item $TN$: A sentence correctly identified by \tool\ as not a constraint sentence.
	\item $FN$: A sentence incorrectly identified by \tool\ as not a constraint sentence.
\end{enumerate}

@@

\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline API & Methods & Sentences & Spec Sentences & \tool\ Ann & TP & FP & FN & P(\%) & R(\%) & F-Score(\%) \\
\hline 
\hline java.io &  & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 \\ 
\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 \\ 
\hline Total &  & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ \\ 
\hline
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{6.5in}}{\footnotesize $^*$ Column average; TP: Total number of True Positives; 
FP: Total number of False Positives; FN: Total number of False Negatives; P: Precision; R: Recall} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

\subsubsection{RQ1: Effectiveness in Identifying Specification Sentences}

In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying constraint sentences.
Column ``API'' lists the names of the subject API. 
Column ``Methods'' and ``Sentences'' lists the number of methods and sentences in each subject API's.
Column ``\tool\ Ann'' lists the number of sentences identified by \tool\ as constraint sentences. 
Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
Columns ``P(\%)'', ``R(\%)'', and ``F-Score(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.

@@

Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure and/or inadequacy of generic dictionaries for synonym analysis. For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}'' from the \CodeIn{close} method description from \CodeIn{FileOutputStream}. The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint. However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''. This incorrect matching in turn causes \tool to incorrectly annotate the sentence as constraint sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}. We observed 8 instances of previously described example in our results.

If we manually fixed the Wordnet dictionaries to match ``has'' and ``get'' as synonyms, our precision is further increased to 70.8\% effectively increasing the F-Score of \tool to 71.2\%. We refrained from including such modifications for reporting the results to stay true to our proposed framework. In the future, we plan to investigate techniques to construct better domain dictionaries for software API.

We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative). False negatives are undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents. Furthermore, an overwhelming number of false negatives works against the usefulness of \tool. For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. The sentence describes the constraint in terms of invoking the same method again. Although \tool\ correctly identifies the method \CodeIn{close} in the sentence, \tool\ currently does not support temporal constraint on the same method. Aforementioned, limitation causes \tool\ to not identify the statement as a constraint constraint.

@@

In this section, we evaluate the effectiveness of \tool\ in inferring constraint sentences from API documents.

If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object), those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.

If markposMM is -1MM (no mark has been set or the mark has been invalidated), an IOExceptionMM is thrown.

@@

@@

Threats to internal validity include the correctness of our implementation in extracting usage constraints and labelling a statement as a constraint statement. To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation. Furthermore, we ensured that the results were individually verified and agreed upon by two authors.

>>>>

\begin{enumerate}
	\item $TP$: A sentence correctly identified by \tool\ as constraint sentence.
	\item $FP$: A sentence incorrectly identified by \tool\ as constraint sentence.
	\item $TN$: A sentence correctly identified by \tool\ as not a constraint sentence.
	\item $FN$: A sentence incorrectly identified by \tool\ as not a constraint sentence.
\end{enumerate}

@@

\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
\hline 
\hline java.io &  & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
\hline Total &  & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
\hline
%----------------- END TABLE DATA ------------------------ 
\multicolumn{13}{p{6.5in}}{\small
$^*$ Column average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences;
Sen$_{ICON}$: Total no. of constraint Sentences identified by \tool; 
TP: Total no. of True Positives; FP: Total no. of False Positives; FN: Total no. of False Negatives;
P: Precision; R: Recall; F$_S$: F-Score; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

\subsubsection{RQ1: Effectiveness in Identifying Constraint Sentences}

In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying constraint sentences.
Column ``API'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' lists the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' list the number of manually identified constraint sentences.
Column ``Sen$_{ICON}$'' lists the number of sentences identified by \tool\ as constraint sentences. 
Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
Columns ``P(\%)'', ``R(\%)'', and ``F$_S$(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.

@@

Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure and/or inadequacy of generic dictionaries for synonym analysis. For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}'' from the \CodeIn{close} method description from \CodeIn{FileOutputStream}. The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint. However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''. This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}. We observed 8 instances of previously described example in our results.

If we manually fixed the Wordnet dictionaries to match ``has'' and ``get'' as synonyms, our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%. We refrained from including such modifications for reporting the results to stay true to our proposed framework. In the future, we plan to investigate techniques to construct better domain dictionaries for software API.

We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative). False negatives are undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents. Furthermore, an overwhelming number of false negatives works against the usefulness of \tool. For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}'' from  \CodeIn{PUT Object-Copy} method description in \amazonAPI. The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object}) before calling the current method. However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.

@@

In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents. To answer RQ2, we ran the sentences manually identified as constraint sentences against \tool. We then manually verified the correctness of temporal constraints inferred by our \tool. We define the \CodeIn{accuracy} of \tool\ as the ratio of constraint sentences with correctly inferred temporal constraints to the total number of constraint sentences.

Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
Column ``API'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' lists the number of manually identified constraint sentences.
Column ``Spec$_{ICON}$'' lists the number of sentences with correctly inferred temporal constraints by \tool. 
Column ``Acc(\%)'' list percentage values of accuracy. 
Our results show that, out of 90 manually identified constraint sentences, \tool\ correctly infers temporal constraints with the average accuracy of 70.0\%.

We next present an example to illustrate how \tool\ incorrectly infers temporal constraints from a constraint sentence. Consider the sentence ``if the stream does not support seek, or if this input stream has been closed by invoking its close method, or an I/O error occurs.'' from \CodeIn{skip} method of \CodeIn{java.io.FilterInputStream} class. Although \tool\ correctly infers that close cannot be called before current method, \tool\ incorrectly associates the phrase ``support seek'' with method \CodeIn{markSupported} in the class. The faulty association happens due to incorrect parsing of the sentence by the underlying NLP infrastructure. Such issues will be alleviated as the underlying NLP infrastructure improves.

Another, major cause of failure for \tool\ in inferring temporal constraints from sentences is the failure to identify the sentence as a constraint sentences at the first place (false negatives). Overall, accuracy of \tool\ can be significantly improved by lowering the false negative rate in identifying the constraint sentences.

@@

In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\% respectively. Furthermore, we also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%. Furthermore, also provide discussion that a false positives rate and false negatives rate can be further improved by improving the underlying NLP infrastructure. Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system.

@@

Threats to internal validity include the correctness of our implementation in extracting usage constraints and labeling a statement as a constraint statement. To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation. Furthermore, we ensured that the results were individually verified and agreed upon by two authors.

### 2014-03-13 Draft/example.tex
Updated abstract, Intro, eval

We now present some real world examples to motivate our approach. In particular, through these examples, we demonstrate that developers often ignore the tempral specifications of an API present in its documentation. We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
pages. For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages. Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that invoke API methods in sequences prohibited by documentation. 
If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.

@@

Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is a question and answer site for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}.
In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon.
The document clearly states that before deleting the bucket, the objects in the buckets must be deleted. \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}, \textit{(``...paying for excess stuff you don't need is simply idiotic...'')}.

@@

Formal verification tools can be used to easily find such kind of defects.
However, formal analysis tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal or machine understandable format. 
Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation. In next section, we briefly discuss the related work in this area.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{Example2.eps}
\end{center}
\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
\end{figure}

>>>>

We now present a real world example to motivate our approach. In particular, through the example, we demonstrate that developers often ignore the temporal specifications of an API present in its documentation. We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
pages. For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages. Developers may not have time and patience to go through all the documentation and may miss various temporal specifications of the API, resulting in defective applications that invoke API methods in sequences prohibited by documentation. 
If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.

@@

Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is a question and answer site for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}.
In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon.
The document clearly states that before deleting the bucket, the objects in the buckets must be deleted. \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
%In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}, \textit{(``...paying for excess stuff you don't need is simply idiotic...'')}.

@@

Formal verification tools can be used to easily find such defects.
However, formal analysis tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal or machine understandable format.
For instance, a rule can be added to a static checker to ensure presence of a call to delete objects before the call to delete bucket.
Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation. In next section, we briefly discuss the related work in this area.

%\begin{figure}[t]
%\begin{center}
%\includegraphics[scale=0.6]{Example2.eps}
%\end{center}
%\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
%\end{figure}

### 2014-03-13 Draft/introduction.tex
updated evaluation
Updated abstract, Intro, eval

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
\textbf{There are} existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}. 
In contrast, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods. Our proposed approach addresses the following challenges to infer temporal constraints automatically from API documents.

First, relying just on type information will result in an incomplete list of temporal constraints. 
In typed languages some temporal constraints are enforced by type system. 
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from
the natural language text in API documents.
%Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
%for a strongly typed language.
%The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
%Our proposed approach extends the existing approaches to address the challenge.

%identified in previous work~\cite{pandita12:inferring} delete and leave the reference
% Add a sentence stating that we extend previous technique to address the issues 
Second, inferring temporal constraints from the natural language text itself is challenging. 
There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
In addition to these challenges, we have an added challenge of identifying the method referenced in the natural language text to infer temporal constraint.
Recall the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively time and resources intensive.
To address this challenge, we propose to build domain-dictionaries systematically from API documents and generic English dictionaries.

% talk about mining approaches 
In summary, the proposed work leverages natural language description of API's to infer temporal constraints of method invocations.
As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the library.
Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client software that use the API.
The proposed work in general, makes the following contributions:
%However, all of these approaches rely on the availability of the source code that use API methods under investigation.
%Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available.
%To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.

>>>>

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
Although, existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.

Apart from method specifications, Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing. However, temporal specification are not limited to resource usage. Furthermore, their technique fails to make the finer grained distinction on the ordering of the methods within a phase. For the description mentioned in previously, assuming that the method calls are associated with resource ``part'', both the methods referenced are logically associated with the creation phase of resource. Zhong et al.~\cite{zhong09SE} approach fails to make a distinction in ordering of such methods. In contrast our proposed approach leverages natural language processing to infer generic temporal specifications (not limited to resource related constraints) and also improves upon existing work for making finer grained distinction between ordering of methods within a phase of a resource.

%First, relying just on type information will result in an incomplete list of temporal constraints. 
%In typed languages some temporal constraints are enforced by type system. 
%For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
%However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
%We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from
%the natural language text in API documents.
%Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
%for a strongly typed language.
%The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
%Our proposed approach extends the existing approaches to address the challenge.

%identified in previous work~\cite{pandita12:inferring} delete and leave the reference
% Add a sentence stating that we extend previous technique to address the issues 
However, inferring temporal constraints from the natural language text is challenging. 
There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
In addition to these challenges, we have an added challenge of 
implicit method referencing: identifying the method referenced in the natural language text to infer temporal constraint.
Recall the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively time and resources intensive.
To address this challenge, we propose to build domain-dictionaries systematically from API documents and generic English dictionaries.

% talk about mining approaches 
In summary, the proposed work leverages natural language description of API's to infer temporal constraints of method invocations.
As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the API library.
Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client software that use the API.
The proposed work in general, makes the following contributions:
%However, all of these approaches rely on the availability of the source code that use API methods under investigation.
%Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available.
%To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.
